%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}
\usepackage{multicol}

\begin{document}
\header{jacob}{garcia}
       {full stack developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    \href{mailto:mario@nure.mx}{mario@nure.mx}
    +5215581452376
    \href{https://github.com/jacobgarcia}{github.com/jacobgarcia}
    \href{https://angel.co/jacobgarcia}{angel.co/jacobgarcia}
    \href{https://nure.mx}{nure.mx}
    ~
    Mexico City
  \section{languages}
    \textbf{bilingual}
    {spanish/english}
  \section{programming}
    {\color{red} JavaScript
    (ES6, Node, React)}
    MongoDB
    HTML5 \& CSS3
\end{aside}

\section{summary}

Avant-garde mixer of art, science and technology. Complex problem-solver with an \\
analytical and driven mindset. Full-stack developer using MERN technology. Passionate video game builder using Unity and UE.

\section{work history}

\begin{entrylist}
  \entry
    {2017 - now}
    {Connus}
    {Lead Full Stack Developer (MERN)}
    {Web app for monitoring telecommunication sites infrastructure.\\
    Application logic, server-side actions and frontend related tasks.\\
    Database design and modeling. \\
    Code review, testing and debugging.\\
    Architecture, deployment and maintenance. \\
    Continuous training of Junior IT members. \\
    }
\entry
    {2017 - now}
    {Nure}
    {Lead Backend Developer (MERN) - Co-Founder}
    {Digital services, product development and branding agency.\\
    Server-side actions and business application logic.\\
    Customer relationships and financial management. \\
    }
 \entry
    {2016 - 2017}
    {Wetopia}
    {Lead Software Developer (MEAN) - Co-Founder}
    {Technology based company.\\
    CTO and lead software developer.\\
    Embedded computing projects and web applications. \\
    }

\entry
    {2016}
    {Musement}
    {Full Stack Developer (MEAN) - Co-Founder}
    {Web app for sharing work updates and receive feedback.\\
    API programming, backend development and frontend related tasks.\\
    SCRUM Master and project manager.
    }
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {grad. 2017}
    {B.S. in Computer Systems Engineering}
    {Monterrey Institute of Technology}
    {Graduated summa cum laude. \\
    Received highest scholarship available.\\
    Graduated with 97/100 GPA}
\end{entrylist}



\section{web programming skills}

\begin{multicols}{5}
\begin{description}
  \item[$\bullet$] JavaScript
  \item[$\bullet$] ES6
  \item[$\bullet$] NodeJS
  \item[$\bullet$] Express
  \item[$\bullet$] React
  \item[$\bullet$] Redux
  \item[$\bullet$] MongoDB
  \item[$\bullet$] Angular
  \item[$\bullet$] HTML5
  \item[$\bullet$] CSS3
  \item[$\bullet$] Gulp
  \item[$\bullet$] Webpack
  \item[$\bullet$] NGINX
  \item[$\bullet$] AWS
  \item[$\bullet$] SASS
  \item[$\bullet$] SCRUM
\end{description}
\end{multicols}

\section{other programming skills}
\begin{multicols}{2}
\begin{description}
  \item[$\bullet$] Git
  \item[$\bullet$] SQL
  \item[$\bullet$] Python Scripting
  \item[$\bullet$] Java
  \item[$\bullet$] Unity3D
  \item[$\bullet$] Unreal Engine 4
  \item[$\bullet$] C++
  \item[$\bullet$] C Sharp
\end{description}
\end{multicols}

\section{soft skills}
\begin{multicols}{2}
\begin{description}
  \item[$\bullet$] Creative
  \item[$\bullet$] Autodidact
  \item[$\bullet$] Responsible
  \item[$\bullet$] Entrepreneur
  \item[$\bullet$] Team Worker
  \item[$\bullet$] Leader
\end{description}
\end{multicols}


\section{certifications}

\begin{entrylist}
  \entry
    {since 2016}
    {Oracle}
    {Certified Professional}
    {Java SE6 Professional Programmer\\}
  \entry
    {since 2016}
    {CISCO}
    {Certified Network Associate Routing and Switching}
    {CCNA Routing and Switching Essentials \\
    CCNA Introduction Networks}
\end{entrylist}

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
