\cvsection{Projects}
\begin{cventries}
  \cventry
    {Game Programmer}
    {1408}
    {Toluca, Unreal Engine 4}
    {May 2018 - Present}
    {
      \begin{cvitems}
        \item {Developed a full \textbf{real-time day and night cycle} based on the local time of the user. Different light sets for all times. }
        \item {Implemented an in-game chat for real-time communication using private rooms on the \textbf{Socket.io} plugin. }
        \item {Designed a hotel room serving as the main level. Programmed various \textbf{triggers and events} on the environment.}
      \end{cvitems} 
    }
  \cventry
    {Game Programmer}
    {P.L. (Playable Library)}
    {Toluca, Unity 5}
    {Nov. 2015 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Implemented a horror P.T. (Silent Hills) like \textbf{experience} on a 3D modelled school's library creepy environment. }
        \item {Replicated filters and effects using \textbf{post-processing stack} of Silent Hills. Added elements like head animations to the FPS controller. }
        \item {Programmed \textbf{triggers}, \textbf{items}, \textbf{events}, \textbf{particles systems}, \textbf{NPCs} and \textbf{character and environment animations}. }
      \end{cvitems}
    }
    \cventry
    {Graphics Programmer}
    {Doom Processing}
    {Toluca, Processing 3}
    {Sep. 2015 - Oct. 2015}
    {
      \begin{cvitems}
        \item {Developed a simple Doom one-level \textbf{experience}. Shooting, killing enemies, multiple weapons and doors are all available. }
        \item {Programmed an \textbf{FPS controller} from scratch using only \textbf{Java}. Capable of moving on (X, Y) axis, jumping and collision with objects}
        \item {Programmed \textbf{triggers}, \textbf{collisions}, \textbf{sprite sheet animations}, \textbf{enemies} and \textbf{SFX}. Designed level and gampelay features. }
      \end{cvitems}
    }
    \cventry
    {Game Designer \& Programmer}
    {Quadrality}
    {Toluca, Unity 4}
    {Jun. 2014 - Dic. 2014}
    {
      \begin{cvitems}
        \item {Designed gameplay mechanics, characters and levels for a human rights \textbf{3D platformer} web game inspired by the LEGO series. }
        \item {Programmed triggers, \textbf{shaders}, events, animations, particle systems, \textbf{SFX} and \textbf{environmental elements}. Designed \textbf{UI} using \textbf{NGUI}. }
      \end{cvitems}
    }
\end{cventries}
